\chapter{Continuous learning} 
\label{ch:learning}


\section{Explain}
\begin{content}

\begin{remark}
There are three readings, which means that the heart is coming, the eyes are coming, and the mouth is coming. - Zhu Xi, "The Training Regulations"
\end{remark}

When I was born, my father named me \emph{Liu Guangyun}, Cheng \quo{光} generation, word \quo{云}. But since I went to school, I don’t know what it is. One day, the Chinese teacher said that the text explained: \quo{Cong, ears, eyes, mouth, heart is also}. I feel that I have a special liking for the \quo{聪} word, and I changed my name to \emph{刘光聪}.

It’s also a coincidence that since then, my mother has never worried about my studies.


\subsection{Select}
Ear to the ear, choose the good person from it, choose the one who is not good and change it. Some people are accustomed to giant functions, big logic, why are they so, and their names are: for the effect of \ascii{(hai)} rate\ascii{(zi)}; and I prefer a layered code style. Short and lean, with clear intentions.

The experience of others is important, but we need to receive it selectively, not blindly. Don't be fascinated by the master, the master sometimes makes mistakes. The key lies in self-reflection and good at discerning. Especially in this impetuous world, those who can run on the ground are calling \quo{master}.


\subsection{Abstract}
Seeing, sweeping the exceptions, straightforward. What you can see at a glance is an illusion. You can't see it. It's often the essence that you can't touch. Some people are accustomed to the logic of flattening and letting them repeat; and I prefer abstraction and regard the process of revealing the essence as a kind of enjoyment.

Abstraction, of course, has complexity. But such complexity is contextual. If you have similar experience, abstraction becomes a pattern. That is a kind of beauty, a medium of communication.

If the other party lacks context, abstraction is naturally difficult. The so-called simplicity is the revealing of the nature of the problem, and it pays the least price for it; instead of being flat and straightforward, simplicity is the beauty that those outsiders can never feel.

Too late, blind abstraction, will inevitably increase unnecessary complexity. It is like a large-scale pre-design, talk about the various needs of customers, talk about various changes in software design, blind abstraction.


\subsection{Share}
Oral, preaching, teaching, and confusing. Sharing is a belief in life. When you understand sharing, you naturally understand the meaning of existence. I like to share my knowledge and use it as a learning motivation to urge myself to thoroughly understand the nature of the problem.

Because of the ability to share, knowledge naturally becomes something of its own. Daily \ascii{Code Review}, I often encourage team members to actively share, one to promote the team without differences, and the other to help the sharer thoroughly understand the nature of the problem.

The key to convincing others is to give others reasons to be convinced. While sharing, it can help to exercise your expressive ability, which takes a long time \emph{deliberate practice}.


\subsection{Comprehension}
When you are in your heart, you can learn and think, and you can get it if you don’t think about it. Only through independent thinking and summing up the knowledge that is truly your own.

I prefer to use charts to summarize knowledge. On the one hand, the expressive power of the graph is far greater than that of the text; in addition, by drawing, it is also forced to thoroughly understand the nature of the problem.

\end{content}


\section{The road to growth}
\begin{content}


\subsection{Deduplication}
The code needs to eliminate duplication, and the habit of working also eliminates duplication. Don't be stuck with the inherent working conditions. Repeated working conditions often make people fall into a comfortable illusion and fall into the crisis of \emph{three-year effect}.


\subsection{Refining knowledge}
First of all, we are not learning information, but knowledge. Knowledge is valuable, and information has no value. It is only through your own screening, refining, and summarization that information can be turned into knowledge.


\subsection{Become a habit}
Knowledge is easy to forget. Only by putting knowledge into action and integrating it into your own work state can you become your own property forever.

For example, the use of shortcut keys, do not deliberately remember, but become a work habit of yourself; do not repeat the labor, use \ascii{Shell} to provide automation, let \ascii{Shell} become work efficiency The weapon will become a work habit.


\subsection{Update Knowledge}
We need to constantly update existing knowledge systems, especially in an era of knowledge explosion. I hate those who believe in dogma. To give a simple example, old code specifications often require \code{YODA Notation} idioms like \code{if (NULL != p)}. But such an expression compiler is happy, but it is very unfriendly to programmers.

\ascii{\quo{if you are at least 18 years old}} is more in line with English expression habits than \ascii{\quo{if 18 years is less than or equal to your age}}.

Some people refute this idiom, but modern compilers often report warnings for such misuse; and keep the pace of development of \ascii{TDD}, small steps forward, such low-level errors are hard to escape from the French Open.


\subsection{Refactoring self}
Learn, then know enough; teach, then know sleepy. Don't stay at the origin, you should always refactor your knowledge system.

When I first started designing \ascii{OO}, I had nowhere to design patterns; because all the books I saw were about how well the design pattern was. Until I saw some ideas from evolutionary design, simple design and over-engineering, let me return to reason.


\subsection{Specialized in practice}
People's energy is limited, and one cannot grasp all the knowledge in the world. Rather than hesitating in the choice of programming language, it is better to thoroughly understand the inherent nature of methodology; rather than being unresolved in many frameworks, it is better to focus on the problem itself.

In short, Bo is not refined, it must be prevented.
\end{content}
